GPU Efficient Texture Based Bezier Curve Evaluation

### 2015-08-13 Paper/paper.tex
2nd Performance Data Point.  Ready for Blizzard Review

\begin{tabular}{|l|l l|}
\hline
& \multicolumn{2}{|c|}{NV GF GTX 980m} \\
& \bf{HW} & \bf{SW}\\ \hline
\bf{1D Texture / Linear Curve} & 131.8 $\mu$s & 132.7 $\mu$s \\ \hline
\bf{2D Texture / Quadratic Curve} & 131.1 $\mu$s & 135.1 $\mu$s \\ \hline
\bf{3D Texture / Cubic Curve} & 135.4 $\mu$s & 146.2 $\mu$s \\ \hline
\end{tabular}

TODO: Test with at least one other card

The performance characteristics don't change very much based on texture dimensionality. This shows that you can up the degree of the curve by upping the dimension of the texture you store the curve in, without incurring any significant performance costs.

>>>>

\begin{tabular}{|l|l l|l l|}
\hline
& \multicolumn{2}{|c|}{NV GF GTX 980m} & \multicolumn{2}{|c|}{NV GF GTX 770}\\
& \bf{HW} & \bf{SW} & \bf{HW} & \bf{SW} \\ \hline
\bf{1D Texture / Linear Curve} & 131.8 $\mu$s & 132.7 $\mu$s & 103.0 $\mu$s & 104.1 $\mu$s \\ \hline
\bf{2D Texture / Quadratic Curve} & 131.1 $\mu$s & 135.1 $\mu$s & 104.1 $\mu$s & 118.2 $\mu$s \\ \hline
\bf{3D Texture / Cubic Curve} & 135.4 $\mu$s & 146.2 $\mu$s & 104.1 $\mu$s & 130.1 $\mu$s \\ \hline
\end{tabular}

The performance characteristics don't change very much based on texture dimensionality. This shows that you can up the degree of the curve by upping the dimension of the texture you store the curve in, without incurring any significant performance costs.  While software implementations are a bit slower, they are not significantly slower.  Again, the usage case for deciding whether to offload curve work to the sampler (and if so, how much of it), or to do it in the shader program depends on your specific circumstances, and the resource usage of your application.
